Multi-objective autotuning of MobileNets\\ across the full software/hardware stack

### 2018-06-12 dissemination.publication/08da9685582866a0/paper.tex
improved meta for ACM DL proceedings
added ISBN
Clarify that the accuracy claim was made by the MobileNets authors.

% ISBN
\acmISBN{}

@@

  \item The colour of a marker denotes the execution engine: TensorFlow on the CPU or the ArmCL on the GPU.

@@

Moreover, the measured accuracy is up to $0.8\%$ lower than the accuracy
claimed for the same set of weights.
%
We speculate that this discrepancy is due to a difference in preprocessing of
input images.

>>>>

% ISBN
\acmISBN{978-1-4503-5923-8}

@@

  \item The colour of a marker denotes the execution engine: TensorFlow on the CPU or ArmCL on the GPU.

@@

Moreover, the measured accuracy is up to $0.8\%$ lower than the accuracy
that the MobileNets authors claimed for the same set of weights.
%
We speculate that this discrepancy is due to a difference in preprocessing of
input images.
